EuringPosterFigures

### 2021-05-04 scripts/EuringPosterFigures.Rmd
created figures for bias by parameter (adult survival, juv survival, fec)

library(tidyr)
library(dplyr)
library(cowplot)
library(ggplot2)
library(coda)
library(captioner)
library(knitr)
library(reshape2)
library(here)
library(RColorBrewer)
```

@@

ggplot(phi1.plot.vals, aes(x = factor(phi1_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Juv survival') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

>>>>

library(tidyr)
library(dplyr)
library(cowplot)
library(ggplot2)
library(coda)
library(captioner)
library(knitr)
library(reshape2)
library(here)
library(RColorBrewer)
library(colorspace)
```

@@

ggplot(phi1.plot.vals, aes(x = factor(phi1_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Juv survival') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x',
             labeller = ) +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

```{r phiad}
pal1 <- diverging_hcl(n = 7, palette = "Blue-Yellow 3")
phiad <- rel.bias.vals %>% filter(variable == 'Adult survival')
summary(phiad$value)

p1 <- ggplot(rel.bias.vals %>% filter(variable == 'Adult survival'), 
             aes(x = factor(phiad.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Adult Survival') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#9FA2FF", high = "#BAAE00", midpoint = 0,
                      breaks = c(-0.15, -0.05, 0, 0.05), n.breaks = 4, labels = c("-0.15", "-0.05", "0", "0.05")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Adult Survival")
p1
```

```{r phijuv}
pal2 <- diverging_hcl(n = 7, palette = "Green-Orange")
phi1 <- rel.bias.vals %>% filter(variable == 'Juv survival')
summary(phi1$value)

p2 <- ggplot(rel.bias.vals %>% filter(variable == 'Juv survival'), 
             aes(x = factor(phi1.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Juvenile Survival') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#11C638", high = "#EF9708", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2, 0.5, 0.8), n.breaks = 5, 
                      labels = c("-0.2", "0", "0.2", "0.5", "0.8")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Juvenile Survival")
p2
```

```{r fec}
pal3 <- diverging_hcl(n = 7, palette = "Cyan-Magenta")
fec <- rel.bias.vals %>% filter(variable == 'Fecundity')
summary(fec$value)

p3 <- ggplot(rel.bias.vals %>% filter(variable == 'Fecundity'), 
             aes(x = factor(fec.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Fecundity') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0,
                      breaks = c(-0.4, -0.2, 0, 0.2), n.breaks = 4, 
                      labels = c("-0.4", "-0.2", "0", "0.2")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Fecundity")
p3
```

```{r combo}
library(patchwork)
plot1 <- p1 / p2 / p3
plot1

## export out
pdf(here("figures", "params_bias.pdf"), width = 12, height = 8)
plot_grid(p1, p2, p3, nrow = 3)
dev.off()
```
